---
title: "Content & Deliverables"
format: html
editor: visual
---

# Project 1 - Capstone Deliverables

This is a sample page where you can archive project deliverables. Every header you use will correspond to a tab in the legend - shown on the right-hand side of your screen ("On this page").

If you've produced any GIS layers for your 599 project, this may be a good place to share them as interactive maps through leaflet. Alternatively, you can upload high-res figures showing correlations, box-plots, etc. from your report here, and provide a brief overview of key project results. If you have written some useful functions, you may also want to share those here to demonstrate proficiency in particular coding languages or synergies between notable coding packages.

## Leaflet

Sample leaflet - for detailed leaflet instructions, visit the FCOR 599 workshop archive page [here](https://ubc-mgem-fcor599.github.io/FCOR-599-Workshops/Interactive_Maps/leaflet.html).

```{r leaflet, include = FALSE}
library(dplyr); library(leaflet)

m <- leaflet() %>%
  addProviderTiles("Esri.WorldImagery") %>%
  addScaleBar(position = c("bottomleft")) %>%
  setView(-123.1207, 49.2827, zoom = 11)

```

```{r map, echo=FALSE}
m
```

## Code Snippets

Sample code snippet. Notice that you can provide a toggle to switch between coding languages - this is referred to as a 'tabset' in quarto. It is good practice to try and convert your R code to python, and vice-versa to demonstrate coding proficiency. For example, let's showcase a function for calculating NDVI in R and Python.

::: {.panel-tabset group="language"}
## R

``` (.r)
calc_ndvi <- function(nir, red){ ndvi <- (nir-red)/(nir+red) return(ndvi) }
```

## Python

``` (.python)
def calc_ndvi(nir, red): 
  ndvi = (nir.astype(float)-red.astype(float))/(nir.astype(float)+red.astype(float))
  return(ndvi)
```
:::

## Web maps

```{=html}
<iframe width="900" height="700" src="https://utoronto.maps.arcgis.com/apps/View/index.html?appid=afe58019bf384ded937c2943d20261b8" title="Lost Rivers Demo"></iframe>
```

## Urban ecology: Stream temperature as a function of impermeable land cover

Increased impermeable surface cover increases runoff and temperatures in urban streams with
ecological implications. Analysis of impermeable surface area at sites in Toronto region watersheds
was carried out to test the relevance of this relationship. Surface impermeability is correlated with
mean stream temperature at large scales, but minimum and maximum temperatures display no
relationship. This may be due to the homogeneous urban landscape, the impact of cool water entering upstream at headwaters, or other physical characteristics of urban streams.
